### 2023-04-13 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

The biggest motivation to use EHDA is to have a more precise and uniform size and shape of droplets creation.

EHDA research has contributed as an important tool for the development of technology. 
Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is done empirically and based on average current measurements.
The flowing electrical current carried by the spray reveals characteristic shapes for different atomization modes.
These forms cannot simply be summarized by their average value. In figure one we can see an example of cone-jet electrospray mode.

Figure 1: example of EHDA

Signal processing techniques may allow non-visual classification of spray mode based on electrical current form. 
The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
Industrial applications require automated stabilization of a spray mode. 
This can be achieved by a closed system loop control system. 
Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.

@@

In view of the above, this project aims to:

\begin{enumerate}[a)]
\item multipurpose applications both scientific and industrial application.
\item Fully automated and intuitive system for EHDA research and industrial application.
\item Real Time non-visual classification.    
\item Control and stabilization of desired spraying modes.   
\item System Portability.
\end{enumerate}

% The content of this section may overlap somewhat with that of the previous section, and it may be a summary of the points made above. 
% The choice of section title may be more appropriate for the project proposal phase. 
% After all, at this stage the objectives are known and not the results. 
% On the other hand, it makes little sense to discuss objectives when the project is finished, especially if those objectives have not been achieved.

@@

Signal processing implementations from previous projects from the NHL Stenden Water Technology group are showing good ranking results. 
More research is necessary to improve classification accuracy and research and implementation of proper classification algorithm. 
Because of this, the work will be done by the Water Technology Group at NHL Stenden University of Applied Sciences and in combination with Dutch companies to combine analysis possibilities with knowledge and availability of infrastructure.

>>>>

EHDA research has contributed as an important tool for the development of technology. 
The advantage of using EHDA is precision and uniform size and shape of droplets creation. Specially in certain spraying modes.

Although there are applications of EHDA in industry, the stabilization of the conical jet spray mode is mostly done empirically and based on average current measurements.

The flowing electrical current carried by the spray reveals characteristic shapes for different atomization modes.
Signal processing techniques may allow non-visual classification of spray mode based on electrical current form.

The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
Industrial applications require automated stabilization of a spray mode. 
This can be achieved by a closed system loop control system. 
Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.

@@

This project aims to give continuity to the previous student work\cite{Monica}, 
Mônica, who foccused in detecting undesired discharges (sparks) in the system accusing high eletric potential. 
For that, she developed a python software routine to connect most of the peripherals and analysed the current data.
Her work corroborate the validation of this project motivating its development and optimization.

Above is shown the main goals listed:

\begin{enumerate}[a)]
\item multipurpose applications both scientific and industrial application.
\item Fully automated and intuitive system for EHDA research and industrial application.
\item Real Time non-visual classification of spraying modes.
\item Control and stabilization on a desired spraying mode.   
\item System Portability and versatility.
\end{enumerate}

@@

The NHL Stenden Water Technology group has been involved in previous projects that have successfully implemented automated signal processing techniques, resulting in highly ranked outcomes. 
However, further research is required to enhance the accuracy of the classification algorithm. In order to achieve this, the Water Technology Group at NHL Stenden University of Applied Sciences, in collaboration with Dutch companies, is conducting extensive research and implement appropriate classification algorithms. The aim is to combine analytical capabilities with infrastructure knowledge and availability to achieve optimal results.
As a student from UFMG, I am now actively involved in this research project to improve the automation usability, classification accuracy and system stabilization with signal processing techniques.

\section{Document Structure}
\label{sec:doc_struct}

### 2023-04-13 Documentation/UFMG/PFCII/acknowledgment/acknowledgment.tex
documentation

I wish a big thanks to my mother who always supported me and made me believe in my potential. Teaching me dedication, patience and discipline.
To my father who taught me not to be satisfied and always looking for more, that's what I call ambition and energy to always try to get out of the comfort zone.
To my dear friends from República Casassanta for making university life such a unique and unforgettable moment.

>>>>

I would like to express my heartfelt gratitude to the following individuals and institutions who have played a significant role in shaping me into the person I am today:

First and foremost, my beloved mother, whose support and belief in my potential has been my guiding light throughout my life. Her invaluable lessons on dedication, patience, and discipline have helped me overcome countless challenges and achieve my goals.

I also extend my gratitude to my father, whose teachings on the virtues of ambition have inspired me to strive for excellence. His relentless pursuit of success has been a constant source of energy for me.

I would like to acknowledge the outstanding education and training that I received from the UFMG university, which has equipped me with the necessary skills and knowledge to thrive in the global marketplace. I am grateful for the transformative experience that has prepared me for a fulfilling career and a meaningful life.

Moreover, I cannot forget my dear friends from República Casassanta, who have made my student life such a unique and unforgettable moment. Their camaraderie and support have been a source of joy and comfort during challenging times.

Lastly, I would like to thank myself for having the courage and resilience to pursue my dreams despite my anxieties and doubts. Through my perseverance, I have been able to savor every moment of my journey and give my best to achieve my goals.
